---
title: "da-ws-03-2"
author: Maite Lezama Valdes, Lukas Ditzel, Jannis Gottwald, Alexander Jorns, Michaela
  Vorndran
date: "5 November 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Look and learn
### da-ws-03-1
```{r }
setwd("E:/16_11_1_DA")
df<-read.table("hessen_holzeinschlag_1997-2014.csv", skip = 4, header=T, sep=";", dec =",")
class(df)

# data frame ohne Zeile 19
df<-df[-19, ]
df
summary (df)
write.table(df, "hessen_holzeinschlag_1997-2014_clean.csv", dec=".", sep=",")

```
### da-ws-03-2
####1:
#####Create a simple visualization which gives a quick, temporally non explicit and descriptive statistical overview of the harvest by tree type and as a total over all trees (i.e. a similar kind of information the `summary` function provides).
```{r }
summary (df)
df1 <- df
df2 <- df
attach(df2)

box<-boxplot(df1, xlab="Species", 
ylab="Logging per year in Tsd.", main= "Logging Overview", names = colnames(df1), 
col = (c("green", "green","darkgreen", "darkgreen", "green", "red")))

```





####2: 
#####Have a look at beech and spruce and write exactly one sentence for each of the tree species which summarizes what you see. 

The interquartil range of Beech harvest is relatively small lying between 1500 and 1800, the distribution being left skewed.
In comparison spruce shows a higher variation in quantities harvested, interquartil range of the right-skewed distribution lies between about 1700 and 2600 with an outlier at about 6500.

####3: 
#####Create another visualization which - in the same figure panel - shows how each beech harvest over the time span is related each of the oak, pine, spruce and colored wood harvests in a 2 by 2 grid (i.e. arrange the figures in a 2 columns and 2 rows layout).

```{r }
be<- cbind(Buche,Eiche)
bf<- cbind(Buche, Fichte)
bk <-cbind(Buche, Kiefer)
bb <-cbind(Buche, Buntholz)
par(mfrow=c(2,2), xpd=NA)
matplot (FWJ, be, type ="o", pch=1, main = "logging beech/oak", ylab = "logging in tsd.",xaxt="n")
axis(1, at=c(1997:2014))
matplot (FWJ, bf,type ="o", pch=1, main="logging beech/spruce",ylab = "logging in tsd.", xaxt="n")
axis(1, at=c(1997:2014))
matplot (FWJ, bk, type ="o", pch=1, main="logging beech/pine",ylab = "logging in tsd.", xaxt="n")
axis(1, at=c(1997:2014))
matplot (FWJ, bb, type ="o", pch=1, main= "logging beech/colored wood",ylab = "logging in tsd.",xaxt="n")
axis(1, at=c(1997:2014))
legend("topleft", inset=c(-0.5,-1.2), legend = c("Beech","Other Species"), horiz=F, col=1:2, pch=1, title= "Legend", lty = c(1,2))


#or

l<- list(be, bf, bk, bb)
for (i in l) {matplot (FWJ, i, type ="o", pch=1, main= "Logging", ylab = "Logging in tsd.",xaxt="n")
  axis(1, at=c(1997:2014))}
legend("topleft", inset=c(-.5,-1.2), legend = c("Beech","Other Species"), horiz=F, col=1:2, pch=1, title= "Legend", lty = c(1,2))

```

####4:
#####Describe each plot with exactly one sentence.

The harvest of oak isn't varying much over time and is much less than Beech, which is slightly increasing over time.
Colored wood harvest is zero after the first years, so there can't be made any useful statement about their relation.
The distribution of spruce harvest over time is best correlated with Beech in comparison to the other species, spruce being harvested more in the middle of the timeline.
Pine is being harvested less than Beech with no specific trend to be seen over time. 

